|

### 2020-07-20 paper.Rmd
Figure specifications to get label.

```{r circles, fig.cap="Rescaled equidistant concentric circles, for $p=2, 3, 10, 100$. The circles remain equidistant for $p=2$ where no transformation is performed, and get pushed out towards the edge as $p$ increases."}

>>>>

```{r circles, fig.cap="Rescaled equidistant concentric circles, for $p=2, 3, 10, 100$. The circles remain equidistant for $p=2$ where no transformation is performed, and get pushed out towards the edge as $p$ increases.", out.width="75%", fig.align = "center"}
